Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-22 paper.tex
introduccion modificada

\section{\uppercase{Introduction}}
\label{sec:introduction}
The use of coprocessor and accelerators has been continuously
growing in the past several years and 90 supercomputers
were equipped with accelerators of some sort in the most
recent TOP500 list~\cite{nov14top500}, dated June 2015.
These devices achieve better performance than traditional processors for
codes which match their architecture.

@@

Nowadays, many cloud vendors have started offering virtual machines (VM) with GPUs in order to provide
GPGPU computation service to users who need it. An examples of that are:
Amazon Web Services (AWS)\footnote{\url{https://aws.amazon.com}}, 
Penguin Computing\footnote{\url{http://www.penguincomputing.com}}, 
Softlayer\footnote{\url{http://www.softlayer.com}} and 
Microsoft Azure\footnote{\url{https://azure.microsoft.com}}.
In the public scope, one of the most popular cloud vendors is AWS that has a wide range of preconfigured instances ready to be launched.
Otherwise, owning the propper infrastructure, a private cloud can be deployed using a specific middleware such as
Openstack\footnote{\url{https://www.openstack.org}} or Opennebula\footnote{\url{http://opennebula.org}}.

>>>>

\section{\uppercase{Introduction}}
\label{sec:introduction}
Nowadays, many cloud vendors have started offering virtual machines (VM) with GPUs in order to provide
GPGPU computation service to users who need it. An examples of that are:
Amazon Web Services (AWS)\footnote{\url{https://aws.amazon.com}}, 
Penguin Computing\footnote{\url{http://www.penguincomputing.com}}, 
Softlayer\footnote{\url{http://www.softlayer.com}} and 
Microsoft Azure\footnote{\url{https://azure.microsoft.com}}.
In the public scope, one of the most popular cloud vendors is AWS that has a wide range of preconfigured instances ready to be launched.
Otherwise, owning the propper infrastructure, a private cloud can be deployed using a specific middleware such as
Openstack\footnote{\url{https://www.openstack.org}} or Opennebula\footnote{\url{http://opennebula.org}}.

@@
